Design, Implementation, and Evaluation of Open Power Quality

### 2020-08-03 manuscript.v6/energies-864131.tex
v6 changes.

%=================================================================
% Full title of the paper (Capitalized)
\Title{%The paper was slightly modified by our English editor, please check the whole text and confirm if your meaning is retained; 2.	Do not delete any comment we left for you and reply to each comment so that we can understand your meaning clearly; 3.	If you need to revise somewhere in your paper, please highlight the revisions to let us know. (Thank you for your cooperation in advance.)  (CONFIRMED)
\highlight{Design}, Implementation, and Evaluation of Open Power Quality}

% Authors, for the paper (add full first names)
\Author{\hl{Anthony} %Please carefully check the accuracy of names and affiliations. (CONFIRMED)
J. Christe, Sergey Negrashov and Philip M. Johnson *}

@@

\highlight{{\em 1. We need more renewable energy.}} %Is italics necessary?
 Concerns including pollution, environmental degradation, and~climate change have produced a global movement away from centralized, fossil-fuel-based forms of electrical energy generation and toward distributed, renewable alternatives such as wind and solar. However,~the economic, environmental, and~political advantages of renewable energy come with significant new technical challenges. Wind and solar are intermittent (for example, solar energy cannot be harvested at night) and unpredictable (for example, wind and solar energy fluctuate based upon cloud cover and wind speed). In~addition, renewable energy generation is often distributed throughout the grid (such as in the case of residential rooftop photovoltaic (PV) systems).

@@

\highlight{{\em 2. Traditional top-down monitoring is not well-suited to bottom-up energy generation.}} For traditional grid architectures where generation is centralized and under the complete control of the utility, it is common to monitor power quality only to the substation level, because~it can be assumed that the power quality experienced at the substation is a reasonably accurate proxy for the power quality experienced by the 1000 or so end-users serviced by the substation. Furthermore, if~an end-user experiences a power quality problem not experienced by the substation, then it is most likely due to equipment or electrical issues local to that end-user and not a grid-level~problem.

@@

\highlight{{\em 3. Consumer electronics require high quality power.}} The rise of consumer electronics has raised the bar for what constitutes ``adequate'' power quality. Only a few decades ago, computers were a rare presence outside of labs and large institutions. Today, computers are everywhere: embedded in phones, washers, refrigerators, thermostats, and~so forth. These electronic devices not only have higher power quality requirements, but~some of them actually introduce power quality problems in the form of harmonic distortion. Poor power quality can result in electronic devices failing unpredictably, and/or decreasing their lifespan. Reduced input voltage can cause excessive power supply heat dissipation, resulting in reduced mean time between failures (MTBF). In~addition, rectifiers and DC-to-DC converter switching transistors draw high-peak currents, which raise their junction temperatures. These temperature excursions take a toll on semiconductor longevity. High input voltage can also puncture a power supply's rectifier and switching transistor junctions, causing MTBF reduction and eventual breakdown. High-voltage transients lasting microseconds can permanently wreck the power supply and its electronic equipment load.~\cite{dedad_when_2008}.

\highlight{{\em 4. Power quality data should be publicly available.}} Electrical utilities are not required to be totally transparent about the quality of power they provide to consumers. For~example, in~Hawaii, utilities are only required to make a ``best effort'' to provide non-harmful voltage and frequency values, and~are only required to publicly report about power outages of more than 3 min. There is no requirement for utilities to report potentially harmful levels of voltage, frequency, THD, or~transients as long as they do not lead to outages. Indeed, in~places like Hawaii, there is not yet even infrastructure in place to enable utilities to collect that information, even if they were asked to report on it. Providing a high quality, third party, publicly available source of power quality data not only benefits the public, it makes it much easier to perform research on ways to improve grid stability in the presence of renewable energy~generation.

@@

The power system of the OPQ Box electrically isolates most of the device from the AC mains power.
An isolated AC-DC converter generates $5V_{dc}$ from the mains $120V_{ac}$.
A total of \hl{5 V} is used to power the Raspberry Pi, the~equipment connected to the expansion port, the~3.3 V regulators and voltage reference, and~an isolated DC/DC converter.
A total of 3.3 V is used to power the isolated end of the isolation amplifier as well as the STM32F3 analog to digital converter/digital signal processor (ADC/DSP).
The~hot side of the isolation amplifier is powered from the isolated DC/DC converter.
This allows OPQ Box to function with a battery attached to the expansion port, so that it may retain data and continue to operate during a power~outage.

%%% We added a space between 5 and V. Please confirm. CONFIRMED.

@@

The software stack of the Raspberry Pi aims to deliver an accurate and precise power quality analysis framework despite the rather limited capabilities of the hardware.
A block diagram of the software stack is shown in Figure~\ref{fig:opq:3}.
Digital data is transferred from the DSP to the Raspberry Pi via Serial Peripheral Interface, with~the Pi acting as the master and the DSP as a slave device.
A hardware interrupt line is used to inform Pi software that the DSP is ready for the data transfer, and~a kernel driver provides management of the SPI bus.
Internally, the~OPQ driver maintains a ring buffer of 16 windows, each of which is 200 data samples in size.
Upon receiving the interruption for the DSP, the~CPU sets up the DMA transfer and the DMA engine transfers a 200 sample window into the kernel memory without CPU interaction.
This scheme requires the CPU to only service 60 interruptions a second, with~each interruption requiring on the order of 100 instructions, for~a CPU utilization of less than $1\%$ in normal operation.
Userland applications communicate with the kernel driver using a file descriptor, where every \highlight{$read$} %Is italics necessary here?
 system call yields 200 samples of raw waveform.
As a result, the~smallest window that a userland application may process is a single AC cycle of the grid~mains.

@@

\highlight{{\em Bandwidth usage is minimized.}} % Is italics necessary?
 Instead of sending the entirety of raw data, only extracted features are sent. This results in a tiny fraction of the bandwidth requirement when compared to raw waveforms. Furthermore, the~temporal window, which encompasses a single feature, can be adjusted in real time. Thus, as~soon as an anomalous behavior is observed in a subset of sensors, this window can be adjusted for a finer grained feature~extraction.

\highlight{{\em Effects of latency are minimized.}} In this case, ``latency'' refers to the time required for OPQ Makai to process the incoming feature stream and decide whether to request high fidelity data from one or more OPQ Boxes. Even at 1 M samples/second at 16 bits of resolution, the~memory requirement to store 5 min of raw waveform without compression are on the order of 512 MB, which is well within the realm of inexpensive single board computers such as Raspberry PI. With~compression specifically suited to the signal of interest, the~memory requirement can be reduced even further. In~the case of the OPQ sensor network, OPQ Makai has an hour to process feature data and request high fidelity data from OPQ Boxes. During~our pilot study, OPQ Makai always responded within a second or~two.

\highlight{{\em Cloud processing requirements are reduced.}} Since feature extraction is already performed at the device level, cloud computation requirements are reduced. With~the advent of the Internet of Things, the~computational capacity of edge devices is~increasing.

\highlight{{\em Subthreshold data acquisition can improve understanding of grid-local anomalies.}} OPQ Makai makes the decision to acquire raw waveform from OPQ Boxes. This allows analysis of data from devices that were only mildly affected or even not affected at all by the disturbance. This creates new possibilities for investigation of disturbance propagation across the sensed area, as~will be discussed in Section~\ref{sec:pilot-study}.

\highlight{{\em Temporal locality allows OPQ to provide improved insights into power quality anomalies over traditional triggering algorithms.}} By exploiting the idea of temporal locality, it is possible to ascertain the geographical extent of an anomaly with only coarse features. This allows for a simple robust algorithm, which may be deployed at the sink node for anomaly~detection.

@@

\highlight{{\em Makai Event Actor.}} % Please confirm if this is necessary.
 The Makai Event Actor is responsible for reading data newly created by OPQ Makai into OPQ Mauka. It performs feature extraction on the raw data stream and forwards those features (or the raw data) to subscribing Actor plugins. This allows OPQ Mauka to perform feature extraction once, and~allow use of those features by multiple~Actors.

\highlight{{\em Frequency Variation Actor.}} The Frequency Variation Actor classifies generic frequency sags, swells, and~interruptions as defined by the IEEE 1159 standard. Both duration and deviation from nominal are used to perform these classifications. Duration classifications include frequency deviations that last for less than 50 ns, between~50 ns to 1 ms, and~1 to 50 ms. Classifications for deviations from nominal are performed for values that are up to 40\% deviation from nominal. This Actor is able to classify frequency swells, frequency interruptions, and~frequency sags, leading to the creation of data at the Incident~Layer.

\highlight{{\em IEEE 1159 Voltage Actor.}} The IEEE 1159 Voltage Actor is used to classify voltage Incidents in accordance with the IEEE 1159 standard \hl{[29]}. In~general, this standard classifies voltage disturbances by duration and by magnitude. Voltage durations are classified from 0.5 to 30 cycles, 30 cycles to 3~s, 3 s to a minute, and~greater than 1 minute. Voltage deviations are classified in both the sag and swell directions as a percentage from nominal. Sags are generally classified between 10\% and 90\% of nominal while swells are generally classified from 110\% to 180\% of nominal. This Actor is capable of classifying voltage sags, swells, and~interruptions as defined by the standard, and~creating data at the Incident Layer if~appropriate.
%%% Should it be reference citation? YES
\highlight{{\em Box Optimization Actor.}} The Box Optimization Actor is responsible for sending and receiving typed messages to and from OPQ Boxes from OPQ Mauka. This Actor is capable of requesting the state of each OPQ Box (e.g., uptime, Measurement rate, security keys). It is also capable of adjusting the state of individual OPQ Boxes by changing things such as the Measurement and Trend rate or the sampling rate used by the~Box.

\highlight{{\em Future Phenomena Actor.}} The Future Phenomena Actor is responsible for creating Future or Predictive Phenomena. These Phenomena are used to predict Events and Incidents that may occur in the future. This plugin does not subscribe to any messages, but~instead utilizes timers to perform its work. By~default, this plugin runs every 10~min.

@@

\begin{figure}[H]
\centering
\begin{tabularx}{.4\textwidth}{lX}
\toprule
\textbf{Level} & \textbf{Total} \\
\midrule
Phenomena & 10.4K \\
Incidents & 415K \\
Detections & 91.4K \\
AML (Trends) & 1.94M \\
AML (Measurements) & 116~M \\
IML & 100B \\
\bottomrule
\end{tabularx}
\caption{Entities created at each level of the OPQ Information Architecture during the pilot~study.}
\label{fig:level-statistics}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.4\linewidth]{images/pilot/data-management-graph.png}
\caption{\hl{Storage} requirements with and without~time-to-live (TTL).} %%% It seems that the figure isn't complete, please modify. FIGURE IS COMPLETE.
\label{fig:data-management-graph}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{\hl{For} }%% research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing--original draft preparation, X.X.; writing--review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported. SEE BELOW

\authorcontributions{
Conceptualization, Johnson, Christe, Negrashov; methodology, Johnson, Christe, Negrashov; software, Johnson, Christe, Negrashov; validation, Johnson, Christe, Negrashov; formal analysis, Johnson, Christe, Negrashov; investigation, Johnson, Christe, Negrashov; resources, Johnson; data curation, Christe, Negrashov; writing--original draft preparation, Johnson, Christe, Negrashov; writing--review and editing, Johnson, Christe, Negrashov; visualization, Johnson, Christe, Negrashov; supervision, Johnson; project administration, Johnson; funding acquisition, Johnson. All authors have read and agreed to the published version of the manuscript.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{\hl{Please} }%add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{\hl{Declare} } %conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the results''.

@@

%%% I HAVE ADDED LOCATIONS AND DATES TO FOLLOWING CITATIONS

\bibitem[Trabish(2014)]{trabish_solar_2014}
Trabish, H.
\newblock Solar Installers flee {Hawaii} as Interconnection Queue Backs Up.
\newblock {\em Utility Dive}, {\hl{September 29, 2014}}.%% Please add day month. DONE

@@

\bibitem[Anurangi \em{et~al.}(2017)Anurangi, Rodrigo, and
Jayatunga]{anurangi_effects_2017}
Anurangi, R.O.; Rodrigo, A.S.; Jayatunga, U.
\newblock Effects of high levels of harmonic penetration in distribution
networks with photovoltaic inverters.
\newblock In {Proceedings of the } 2017 {IEEE} {International} {Conference} on IEEE Industrial and {Information} {Systems} ({ICIIS}), Jayapura, Indonesia \hl{November 2, 2017}; pp. 1--6, doi:10.1109/ICIINFS.2017.8300335.%% Please add conference location and date.

@@

\bibitem[Delgado \em{et~al.}(2011)Delgado, Santos, de~Almeida, and
Figueira]{delgado_solutions_2011}
Delgado, J.; Santos, B.; de~Almeida, A.T.; Figueira, A.
\newblock Solutions to mitigate power quality disturbances resulting from
integrating intermittent renewable energy in the grid of {Porto} {Santo}.
\newblock In {Proceedings of the } 11th {International} {Conference} on {Electrical} {Power} {Quality}
and {Utilisation}, Lisbon, Portugal, \hl{October 17, 2011}; pp. 1--6,
\newblock ISSN 2150-6655,
doi:{\changeurlcolor{black}\href{https://doi.org/10.1109/EPQU.2011.6128870}{\detokenize{10.1109/EPQU.2011.6128870}}}.

\bibitem[Zavoda(2018)]{zavoda_power_2018}
Zavoda, F.
\newblock { Power {Quality} and {EMC} {Issues} with {Future} {Electricity}
{Networks}}. In {Proceedings of the } CIGRE, Paris, France, \hl{May 15, 2018}.

\bibitem[Nakafuji \em{et~al.}(2011)Nakafuji, Aukai, Dangelmaier, Reynolds,
Yoshimura, and {Ying Hu}]{nakafuji_back--basics_2011}
Nakafuji, D.; Aukai, T.; Dangelmaier, L.; Reynolds, C.; Yoshimura, J.; {
Hu, Y}.
\newblock “{Back}-to-basics”: {Operationalizing} data mining and visualization
techniques for utilities.
\newblock In {Proceedings of the }The 2011 International Joint Conference on Neural Networks, San Jose, California, \hl{July 31, 2011}; pp. 3093--3098, doi:10.1109/IJCNN.2011.6033630.

\bibitem[Dedad(2008)]{dedad_when_2008}
Dedad, J.
\newblock When {Does} {Poor} {Power} {Quality} {Cause} {Electronics}
{Failures}?
\newblock {\em Electrical Construction and Maintenance Magazine}, {\hl{November 1, 2008}}.
\newblock Library Catalog.  Available online:  \url{www.ecmweb.com} (accessed on \hl{31 July 2020}).

\bibitem[Elphick \em{et~al.}(2015)Elphick, Ciufo, Smith, and
Parera]{elphick_summary_2015}
Elphick, S.; Ciufo, P.; Smith, V.; Parera, S.
\newblock Summary of the economic impacts of power quality on consumers.
\newblock  In {Proceedings of the }2015 {Australasian} {Universities} {Power} {Engineering}
{Conference}, Wollongong, Australia, \hl{September 27, 2015}.

\bibitem[Laskar(2012)]{laskar_power_2012}
Laskar, S.H.
\newblock Power quality issues and need of intelligent {PQ} monitoring in the
smart grid environment.
\newblock In~{Proceedings of the }2012 47th
{International} Universities {Power} {Engineering} {Conference} ({UPEC}), London, England, \hl{September 4, 2012}; pp.~1--6.

\bibitem[Negrashov(2020)]{negrashov_opq_2020}
Negrashov, S.
\newblock {OPQ} {Box} {Specifications} and {Design}, 2020.
\newblock Library Catalog.  Available online:  \url{github.com} (accessed on \hl{31 July 2020}).

\bibitem[Unruh(2018)]{unruh_ieee_2018}
Unruh, T.
\newblock \emph{IEEE P1159/D3: {Draft} {Recommended} {Practice} for
{Monitoring} {Electric} {Power} {Quality}}; IEEE, New York, NY \hl{February 1, 2018}. %% Please provide publisher and its location. DONE

\bibitem[Kahle(2015)]{kahle_power_2015}
Kahle, K.
\newblock Power {Converters} and {Power} {Quality}.
\newblock \emph{arXiv} \textbf{2015}, arXiv:1607.01556. doi:10.5170/CERN-2015-003.57.

\bibitem[Thallam and Heydt(2000)]{thallam_power_2000}
Thallam, R.; Heydt, G.
\newblock Power acceptability and voltage sag indices in the three phase sense.
\newblock In {Proceedings of the } 2000 {Power} {Engineering} {Society} {Summer} {Meeting}, Seattle, Washington,
 \hl{July 16, 2000}; Volume~2, pp. 905--910, doi:10.1109/PESS.2000.867482.

@@

\bibitem[Dickens \em{et~al.}(2019)Dickens, Christe, and
Johnson]{dickens_transient_2019}
Dickens, C.; Christe, A.; Johnson, P.
\newblock A {Transient} {Classification} {System} {Implementation} on an {Open}
{Source} {Distributed} {Power} {Quality} {Network}.
\newblock  In Proceedings of the {Ninth} {International} {Conference} on {Smart}
{Grids}, {Green} {Communications} and {IT} {Energy}-aware {Technologies}, Athens, Greece,
\hl{June 2, 2019}.

\bibitem[Fluke(2020)]{fluke_fluke_2020}
Fluke, I.
\newblock \emph{Fluke {Corporation}: {Fluke} {Electronics}, {Biomedical},
{Calibration} and {Networks}}; \hl{July 31, 2020}.

\bibitem[Dranetz(2020)]{dranetz_dranetz_2020}
Dranetz, I.
\newblock Dranetz {Power} {Monitoring}, 2020.
\newblock Library Catalog. Available online:  \url{ www.dranetz.com} (accessed on \hl{31 July 2020}).

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{
Design, Implementation, and Evaluation of Open Power Quality}

% Authors, for the paper (add full first names)
\Author{Anthony
J. Christe, Sergey Negrashov and Philip M. Johnson *}

@@

\highlight{{\em 1. We need more renewable energy.}}
%%%Is italics necessary? NO. YOU CAN REMOVE THEM.
 Concerns including pollution, environmental degradation, and~climate change have produced a global movement away from centralized, fossil-fuel-based forms of electrical energy generation and toward distributed, renewable alternatives such as wind and solar. However,~the economic, environmental, and~political advantages of renewable energy come with significant new technical challenges. Wind and solar are intermittent (for example, solar energy cannot be harvested at night) and unpredictable (for example, wind and solar energy fluctuate based upon cloud cover and wind speed). In~addition, renewable energy generation is often distributed throughout the grid (such as in the case of residential rooftop photovoltaic (PV) systems).

@@

{\em 2. Traditional top-down monitoring is not well-suited to bottom-up energy generation.} For traditional grid architectures where generation is centralized and under the complete control of the utility, it is common to monitor power quality only to the substation level, because~it can be assumed that the power quality experienced at the substation is a reasonably accurate proxy for the power quality experienced by the 1000 or so end-users serviced by the substation. Furthermore, if~an end-user experiences a power quality problem not experienced by the substation, then it is most likely due to equipment or electrical issues local to that end-user and not a grid-level~problem.

@@

{\em 3. Consumer electronics require high quality power.} The rise of consumer electronics has raised the bar for what constitutes ``adequate'' power quality. Only a few decades ago, computers were a rare presence outside of labs and large institutions. Today, computers are everywhere: embedded in phones, washers, refrigerators, thermostats, and~so forth. These electronic devices not only have higher power quality requirements, but~some of them actually introduce power quality problems in the form of harmonic distortion. Poor power quality can result in electronic devices failing unpredictably, and/or decreasing their lifespan. Reduced input voltage can cause excessive power supply heat dissipation, resulting in reduced mean time between failures (MTBF). In~addition, rectifiers and DC-to-DC converter switching transistors draw high-peak currents, which raise their junction temperatures. These temperature excursions take a toll on semiconductor longevity. High input voltage can also puncture a power supply's rectifier and switching transistor junctions, causing MTBF reduction and eventual breakdown. High-voltage transients lasting microseconds can permanently wreck the power supply and its electronic equipment load.~\cite{dedad_when_2008}.

{\em 4. Power quality data should be publicly available.} Electrical utilities are not required to be totally transparent about the quality of power they provide to consumers. For~example, in~Hawaii, utilities are only required to make a ``best effort'' to provide non-harmful voltage and frequency values, and~are only required to publicly report about power outages of more than 3 min. There is no requirement for utilities to report potentially harmful levels of voltage, frequency, THD, or~transients as long as they do not lead to outages. Indeed, in~places like Hawaii, there is not yet even infrastructure in place to enable utilities to collect that information, even if they were asked to report on it. Providing a high quality, third party, publicly available source of power quality data not only benefits the public, it makes it much easier to perform research on ways to improve grid stability in the presence of renewable energy~generation.

@@

The power system of the OPQ Box electrically isolates most of the device from the AC mains power.
An isolated AC-DC converter generates $5V_{dc}$ from the mains $120V_{ac}$.
A total of 5 V is used to power the Raspberry Pi, the~equipment connected to the expansion port, the~3.3 V regulators and voltage reference, and~an isolated DC/DC converter.
A total of 3.3 V is used to power the isolated end of the isolation amplifier as well as the STM32F3 analog to digital converter/digital signal processor (ADC/DSP).
The~hot side of the isolation amplifier is powered from the isolated DC/DC converter.
This allows OPQ Box to function with a battery attached to the expansion port, so that it may retain data and continue to operate during a power~outage.

@@

The software stack of the Raspberry Pi aims to deliver an accurate and precise power quality analysis framework despite the rather limited capabilities of the hardware.
A block diagram of the software stack is shown in Figure~\ref{fig:opq:3}.
Digital data is transferred from the DSP to the Raspberry Pi via Serial Peripheral Interface, with~the Pi acting as the master and the DSP as a slave device.
A hardware interrupt line is used to inform Pi software that the DSP is ready for the data transfer, and~a kernel driver provides management of the SPI bus.
Internally, the~OPQ driver maintains a ring buffer of 16 windows, each of which is 200 data samples in size.
Upon receiving the interruption for the DSP, the~CPU sets up the DMA transfer and the DMA engine transfers a 200 sample window into the kernel memory without CPU interaction.
This scheme requires the CPU to only service 60 interruptions a second, with~each interruption requiring on the order of 100 instructions, for~a CPU utilization of less than $1\%$ in normal operation.
Userland applications communicate with the kernel driver using a file descriptor, where every \highlight{$read$}
%%%Is italics necessary here? NO, YOU CAN REMOVE THEM.
 system call yields 200 samples of raw waveform.
As a result, the~smallest window that a userland application may process is a single AC cycle of the grid~mains.

@@

\highlight{{\em Bandwidth usage is minimized.}}
%%% Is italics necessary? NO, YOU CAN REMOVE THEM.
 Instead of sending the entirety of raw data, only extracted features are sent. This results in a tiny fraction of the bandwidth requirement when compared to raw waveforms. Furthermore, the~temporal window, which encompasses a single feature, can be adjusted in real time. Thus, as~soon as an anomalous behavior is observed in a subset of sensors, this window can be adjusted for a finer grained feature~extraction.

{\em Effects of latency are minimized.} In this case, ``latency'' refers to the time required for OPQ Makai to process the incoming feature stream and decide whether to request high fidelity data from one or more OPQ Boxes. Even at 1 M samples/second at 16 bits of resolution, the~memory requirement to store 5 min of raw waveform without compression are on the order of 512 MB, which is well within the realm of inexpensive single board computers such as Raspberry PI. With~compression specifically suited to the signal of interest, the~memory requirement can be reduced even further. In~the case of the OPQ sensor network, OPQ Makai has an hour to process feature data and request high fidelity data from OPQ Boxes. During~our pilot study, OPQ Makai always responded within a second or~two.

{\em Cloud processing requirements are reduced.} Since feature extraction is already performed at the device level, cloud computation requirements are reduced. With~the advent of the Internet of Things, the~computational capacity of edge devices is~increasing.

{\em Subthreshold data acquisition can improve understanding of grid-local anomalies.} OPQ Makai makes the decision to acquire raw waveform from OPQ Boxes. This allows analysis of data from devices that were only mildly affected or even not affected at all by the disturbance. This creates new possibilities for investigation of disturbance propagation across the sensed area, as~will be discussed in Section~\ref{sec:pilot-study}.

{\em Temporal locality allows OPQ to provide improved insights into power quality anomalies over traditional triggering algorithms.} By exploiting the idea of temporal locality, it is possible to ascertain the geographical extent of an anomaly with only coarse features. This allows for a simple robust algorithm, which may be deployed at the sink node for anomaly~detection.

@@

\highlight{{\em Makai Event Actor.}}
%%% Please confirm if this is necessary. YOU CAN REMOVE ITALICS.
 The Makai Event Actor is responsible for reading data newly created by OPQ Makai into OPQ Mauka. It performs feature extraction on the raw data stream and forwards those features (or the raw data) to subscribing Actor plugins. This allows OPQ Mauka to perform feature extraction once, and~allow use of those features by multiple~Actors.

{\em Frequency Variation Actor.} The Frequency Variation Actor classifies generic frequency sags, swells, and~interruptions as defined by the IEEE 1159 standard. Both duration and deviation from nominal are used to perform these classifications. Duration classifications include frequency deviations that last for less than 50 ns, between~50 ns to 1 ms, and~1 to 50 ms. Classifications for deviations from nominal are performed for values that are up to 40\% deviation from nominal. This Actor is able to classify frequency swells, frequency interruptions, and~frequency sags, leading to the creation of data at the Incident~Layer.

{\em IEEE 1159 Voltage Actor.} The IEEE 1159 Voltage Actor is used to classify voltage Incidents in accordance with the IEEE 1159 standard \highlight{\cite{bilik_modular_2007}}. In~general, this standard classifies voltage disturbances by duration and by magnitude. Voltage durations are classified from 0.5 to 30 cycles, 30 cycles to 3~s, 3 s to a minute, and~greater than 1 minute. Voltage deviations are classified in both the sag and swell directions as a percentage from nominal. Sags are generally classified between 10\% and 90\% of nominal while swells are generally classified from 110\% to 180\% of nominal. This Actor is capable of classifying voltage sags, swells, and~interruptions as defined by the standard, and~creating data at the Incident Layer if~appropriate.
%%% Please revise the reference order. Reference 29 appears before reference 14. THIS IS A FUNCTION OF LATEX BIBLIOGRAPHY STYLE. PLEASE GO AHEAD AND CHANGE THE REFERENCE ORDER TO YOUR OWN SATISFACTION. I AM NOT CLEAR WHAT IS NEEDED.
{\em Box Optimization Actor.} The Box Optimization Actor is responsible for sending and receiving typed messages to and from OPQ Boxes from OPQ Mauka. This Actor is capable of requesting the state of each OPQ Box (e.g., uptime, Measurement rate, security keys). It is also capable of adjusting the state of individual OPQ Boxes by changing things such as the Measurement and Trend rate or the sampling rate used by the~Box.

{\em Future Phenomena Actor.} The Future Phenomena Actor is responsible for creating Future or Predictive Phenomena. These Phenomena are used to predict Events and Incidents that may occur in the future. This plugin does not subscribe to any messages, but~instead utilizes timers to perform its work. By~default, this plugin runs every 10~min.

@@

\begin{figure}[H]
\centering
\begin{tabularx}{.4\textwidth}{lX}
\toprule
\textbf{Level} & \textbf{Total} \\
\midrule
Phenomena & 10.4~K \\
Incidents & 415~K \\
Detections & 91.4~K \\
AML (Trends) & 1.94~M \\
AML (Measurements) & 116~M \\
IML & 100~B \\
\bottomrule
\end{tabularx}
\caption{Entities created at each level of the OPQ Information Architecture during the pilot~study.}
\label{fig:level-statistics}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.4\linewidth]{images/pilot/data-management-graph.png}
\caption{Storage requirements with and without~time-to-live (TTL).}
\label{fig:data-management-graph}
\end{figure}

@@

\authorcontributions{
Conceptualization, P.M.J., A.J.C., S.N.; methodology, P.M.J., A.J.C., S.N.; software, P.M.J., A.J.C., S.N.; validation, P.M.J., A.J.C., S.N.; formal analysis, P.M.J., A.J.C., S.N.; investigation, P.M.J., A.J.C., S.N.; resources, P.M.J.; data curation, A.J.C., S.N.; writing--original draft preparation, P.M.J., A.J.C., S.N.; writing--review and editing, P.M.J., A.J.C., S.N.; visualization, P.M.J., A.J.C., S.N.; supervision, P.M.J.; project administration, P.M.J.; funding acquisition, P.M.J. All authors have read and agreed to the published version of the manuscript.
}

@@

@@

\bibitem[Trabish(2014)]{trabish_solar_2014}
Trabish, H.
\newblock Solar Installers flee {Hawaii} as Interconnection Queue Backs Up.
\newblock {\em Utility Dive}, {September 29, 2014}.

@@

\bibitem[Anurangi \em{et~al.}(2017)Anurangi, Rodrigo, and
Jayatunga]{anurangi_effects_2017}
Anurangi, R.O.; Rodrigo, A.S.; Jayatunga, U.
\newblock Effects of high levels of harmonic penetration in distribution
networks with photovoltaic inverters.
\newblock In {Proceedings of the } 2017 {IEEE} {International} {Conference} on IEEE Industrial and {Information} {Systems} ({ICIIS}), Jayapura, Indonesia November 2, 2017; pp. 1--6, doi:10.1109/ICIINFS.2017.8300335.

@@

\bibitem[Delgado \em{et~al.}(2011)Delgado, Santos, de~Almeida, and
Figueira]{delgado_solutions_2011}
Delgado, J.; Santos, B.; de~Almeida, A.T.; Figueira, A.
\newblock Solutions to mitigate power quality disturbances resulting from
integrating intermittent renewable energy in the grid of {Porto} {Santo}.
\newblock In {Proceedings of the } 11th {International} {Conference} on {Electrical} {Power} {Quality}
and {Utilisation}, Lisbon, Portugal, October 17, 2011; pp. 1--6,
\newblock ISSN 2150-6655,
doi:{\changeurlcolor{black}\href{https://doi.org/10.1109/EPQU.2011.6128870}{\detokenize{10.1109/EPQU.2011.6128870}}}.

\bibitem[Zavoda(2018)]{zavoda_power_2018}
Zavoda, F.
\newblock { Power {Quality} and {EMC} {Issues} with {Future} {Electricity}
{Networks}}. In {Proceedings of the } CIGRE, Paris, France, May 15, 2018.

\bibitem[Nakafuji \em{et~al.}(2011)Nakafuji, Aukai, Dangelmaier, Reynolds,
Yoshimura, and {Ying Hu}]{nakafuji_back--basics_2011}
Nakafuji, D.; Aukai, T.; Dangelmaier, L.; Reynolds, C.; Yoshimura, J.; {
Hu, Y}.
\newblock “{Back}-to-basics”: {Operationalizing} data mining and visualization
techniques for utilities.
\newblock In {Proceedings of the }The 2011 International Joint Conference on Neural Networks, San Jose, California, July 31, 2011; pp. 3093--3098, doi:10.1109/IJCNN.2011.6033630.

\bibitem[Dedad(2008)]{dedad_when_2008}
Dedad, J.
\newblock When {Does} {Poor} {Power} {Quality} {Cause} {Electronics}
{Failures}?
\newblock {\em Electrical Construction and Maintenance Magazine}, {November 1, 2008}.
\newblock Library Catalog.  Available online:  \url{www.ecmweb.com} (accessed on 31 July 2020).

\bibitem[Elphick \em{et~al.}(2015)Elphick, Ciufo, Smith, and
Parera]{elphick_summary_2015}
Elphick, S.; Ciufo, P.; Smith, V.; Parera, S.
\newblock Summary of the economic impacts of power quality on consumers.
\newblock  In {Proceedings of the }2015 {Australasian} {Universities} {Power} {Engineering}
{Conference}, Wollongong, Australia, September 27, 2015.

\bibitem[Laskar(2012)]{laskar_power_2012}
Laskar, S.H.
\newblock Power quality issues and need of intelligent {PQ} monitoring in the
smart grid environment.
\newblock In~{Proceedings of the }2012 47th
{International} Universities {Power} {Engineering} {Conference} ({UPEC}), London, England, September 4, 2012; pp.~1--6.

\bibitem[Negrashov(2020)]{negrashov_opq_2020}
Negrashov, S.
\newblock {OPQ} {Box} {Specifications} and {Design}, 2020.
\newblock Library Catalog.  Available online:  \url{github.com} (accessed on 31 July 2020).

\bibitem[Unruh(2018)]{unruh_ieee_2018}
Unruh, T.
\newblock \emph{IEEE P1159/D3: {Draft} {Recommended} {Practice} for
{Monitoring} {Electric} {Power} {Quality}}; IEEE, New York, NY February 1, 2018.
\bibitem[Kahle(2015)]{kahle_power_2015}
Kahle, K.
\newblock Power {Converters} and {Power} {Quality}.
\newblock \emph{arXiv} \textbf{2015}, arXiv:1607.01556. doi:10.5170/CERN-2015-003.57.

\bibitem[Thallam and Heydt(2000)]{thallam_power_2000}
Thallam, R.; Heydt, G.
\newblock Power acceptability and voltage sag indices in the three phase sense.
\newblock In {Proceedings of the } 2000 {Power} {Engineering} {Society} {Summer} {Meeting}, Seattle, Washington,
 July 16, 2000; Volume~2, pp. 905--910, doi:10.1109/PESS.2000.867482.

@@

\bibitem[Dickens \em{et~al.}(2019)Dickens, Christe, and
Johnson]{dickens_transient_2019}
Dickens, C.; Christe, A.; Johnson, P.
\newblock A {Transient} {Classification} {System} {Implementation} on an {Open}
{Source} {Distributed} {Power} {Quality} {Network}.
\newblock  In Proceedings of the {Ninth} {International} {Conference} on {Smart}
{Grids}, {Green} {Communications} and {IT} {Energy}-aware {Technologies}, Athens, Greece,
June 2, 2019.

\bibitem[Fluke(2020)]{fluke_fluke_2020}
Fluke, I.
\newblock \emph{Fluke {Corporation}: {Fluke} {Electronics}, {Biomedical},
{Calibration} and {Networks}}; \hl{July 31, 2020}.
%%% Please confirm whether this is a book. Please add published if it is the case.

\bibitem[Dranetz(2020)]{dranetz_dranetz_2020}
Dranetz, I.
\newblock Dranetz {Power} {Monitoring}, 2020.
\newblock Library Catalog. Available online:  \url{ www.dranetz.com} (accessed on 31 July 2020).
